A weighted sampling algorithm for the design of RNA sequences with targeted secondary structure and nucleotides distribution

### 2013-03-12 ISMB/results_ISMB.tex
result completed
remove SSD from supp mat

Before starting our benchmark, we asses the need for our methods and performed an analysis of the \GCContent drift achieved with state-of-the-art software. Using our dataset of $50$ structures, we generated $100$ samples per structure with classical softwares who do not control the \GCContent. Namely,  \RNAinverse, \INFORNA, \NUPACK and \frankenstein.  We show the distribution of the \GCContent of the sequences produced with these softwares in Fig.~\ref{fig:gcdist} those distributions. As anticipated, we observe a clear bias toward high {\GCContent}s and a complete absence of sequence with less than $30\%$ of \GC. This striking results motivates a need for methods that enable to explicitly control the \GCContent and more precisely that enable to design sequences with low \GCContent (i.e. 30\% or less).
}

@@

Next, we show in Figure~\ref{fig:benchmark_RNASSD} the average sequence identity achieved by the various methods. Our results show that at extremely low {\GCContent}s (i.e. 10\%), \ourprog slightly outperforms \RNASSD while this advantage becomes less evident when the \GCContent increases.
}

>>>>

Before starting our benchmark, we asses the need for our methods and performed an analysis of the \GCContent drift achieved with state-of-the-art software. Using our dataset of $50$ structures, we generated $100$ samples per structure with classical softwares who do not control the \GCContent. Namely,  \RNAinverse, \INFORNA, \NUPACK and \frankenstein.  We show the distribution of the \GCContent of the sequences produced with these softwares in Fig.~\ref{fig:gcdist} those distributions.

As anticipated, we observe a clear bias toward high {\GCContent}s and a complete absence of sequence with less than $30\%$ of \GC. This striking results motivates a need for methods that enable to explicitly control the \GCContent and more precisely that enable to design sequences with low \GCContent (i.e. 30\% or less). In order to provide a complete overview of the performance of \ourprog, we provide additional statistics for these software in the supplementary material.
}

@@

Next, we show in Figure~\ref{fig:benchmark_RNASSD} the average sequence identity achieved by the various methods. Our results show that at extremely low {\GCContent}s (i.e. 10\%), \ourprog slightly outperforms \RNASSD while this advantage becomes less evident when the \GCContent increases. Our experiments on higher {\GCContent}s (i.e. 50\% and above) showed that our glocal strategy and the local search approach perform similarly. Similarly, we did not find any clear evidence that a global, local or glocal approach outperforms others when we compare at the thermodynamical stability of the target structure (data not shown).
}

### 2013-03-12 ISMB/supplementary_ISMB.tex
remove SSD from supp mat

\subsection{Benchmark \ourprog vs \RNASSD}
%Using the same dataset of $50$ structures, we generated $100$ samples
%per structure %with \RNAinverse. They yield for most parameters
%a high entropy.
%Table.~\ref{tab:nb_rnainv} contains the number of samples with a given \GCContent generated
%with  \RNAinverse, \INFORNA, \NUPACK and \frankenstein. They have a highly concentrated distribution of \GC content showing one of theirs major deficiencies. We present in Fig.~\ref{fig:gcdist} those distributions.

@@

 For all structures that have been solved 
by the three methods, only \RNASSD, only \texttt{Incarnation} and
\texttt{Incarnation} followed by \RNAinverse, 
we present for different concentration of \GCContent the average sequence identity in Figure.~\ref{fig:identity_50_70_90}
%the average sample entropy and the average base pairs entropy in Figure.~\ref{fig:rnainverse}.
\begin{figure*}[ht!]
  \centering
  \includegraphics[width=\textwidth]{Figures/seq_identity_50_70_90.png}
  \caption{Sequence identity by average \GCContent of $50$, $70$ and $90\%$ for \ourprog,\ourprog+\RNAinverse and \RNASSD.}
  \label{fig:identity_50_70_90}
\end{figure*}
%\begin{table}[h!]
%	\begin{center}
%		\begin{tabular}{|c|ccccc|}
%		\hline
%		Target \GCContent & 10 & 30 & 50 & 70 & 90\\ \hline
%   $\#$\RNAinverse samples& 11 & 437 & 3362 & 1155 & 35\\ \hline
%		\end{tabular}
%	\end{center}
%  \caption{Overall \GCContent distribution for sequences designed using \RNAinverse.}
%	\label{tab:nb_rnainv}
%\end{table}

>>>>

%\subsection{Benchmark \ourprog vs \RNASSD}
%Using the same dataset of $50$ structures, we generated $100$ samples
%per structure %with \RNAinverse. They yield for most parameters
%a high entropy.
%Table.~\ref{tab:nb_rnainv} contains the number of samples with a given \GCContent generated
%with  \RNAinverse, \INFORNA, \NUPACK and \frankenstein. They have a highly concentrated distribution of \GC content showing one of theirs major deficiencies. We present in Fig.~\ref{fig:gcdist} those distributions.

@@

%For all structures that have been solved  by the three methods, only \RNASSD, only \texttt{Incarnation} and \texttt{Incarnation} followed by \RNAinverse, we present for different concentration of \GCContent the average sequence identity in Figure.~\ref{fig:identity_50_70_90}
%the average sample entropy and the average base pairs entropy in Figure.~\ref{fig:rnainverse}.
%\begin{figure*}[ht!]
%  \centering
%  \includegraphics[width=\textwidth]{Figures/seq_identity_50_70_90.png}
%  \caption{Sequence identity by average \GCContent of $50$, $70$ and $90\%$ for \ourprog,\ourprog+\RNAinverse and \RNASSD.}
%  \label{fig:identity_50_70_90}
%\end{figure*}
%\begin{table}[h!]
%	\begin{center}
%		\begin{tabular}{|c|ccccc|}
%		\hline
%		Target \GCContent & 10 & 30 & 50 & 70 & 90\\ \hline
%   $\#$\RNAinverse samples& 11 & 437 & 3362 & 1155 & 35\\ \hline
%		\end{tabular}
%	\end{center}
%  \caption{Overall \GCContent distribution for sequences designed using \RNAinverse.}
%	\label{tab:nb_rnainv}
%\end{table}
